Reduced Nucleotide Diversity on a Plant Y Chromosome Following Recent Recombination Suppression

### 2016-08-21 manuscript.tex
minor edits

For purifying selection simulations, we assumed that selection coefficients followed a gamma distribution, and we considered a range of values for the mean selection coefficient against deleterious mutations ($s$) by varying the scale parameter, $k$ from \X to \X while keeping the distribution shape parameter constant (see Supporting Information for simulation commands). To make the simulation output comparable to our data, we initialized the simulations with our estimated value of $\theta$ (estimated from autosomes), and sampled 8 chromosomes per simulation from 24 populations. For simulating positive selection on the Y, we included a neutral locus of length Ln = 103 bp that is flanked by loci on either side that are subject to selection and are each of length Lf = 105 bp. Simulated sequences also contained 500 kb of linked neutral sequence from which we calculated diversity for each model. We ran 1000 replicates for each model and calculated the average $\theta_{sim}$ and the corresponding Y/A ratio of neutral diversity under the both sets of selection models separately. Finally, we tested the significance of the fit of our simulated diversity output to our empirical data (\X new figure) by calculating the proportion of simulation replicates for which $\theta_{sim}$ was not significantly different from $\theta_{observed}$, using a two-sided P value. Commands for running the simulations are provided in the Supporting Information.

>>>>

For purifying selection simulations, we assumed that selection coefficients followed a gamma distribution, and we considered a range of values for the mean selection coefficient against deleterious mutations, $s$, by varying the scale parameter, $k$ from 0.001 to 0.1 while keeping the distribution shape parameter, $\lambda$, constant (see Supporting Information for simulation commands). To make the simulation output comparable to our data, we initialized the simulations with our empirically estimated autosomal $\theta$, scaled to the  $\theta_{Y}=\theta_{A}/4$ and adjusted for a sex ratio of $N_{m}/N_{f}=0.4$, and sampled 8 haploid chromosomes per simulation from 24 populations. Simulated sequences also contained 500 kb of linked neutral sequence from which we calculated diversity. For simulating positive selection, we included a neutral locus of length $Ln = 103$ bp (\X might change), which was flanked by loci on either side that were subject to positive selection. We ran 1000 replicates for each model and calculated the average $\theta_{Y{sim}}$ and the corresponding Y/A ratio of neutral diversity under the each set of selection models. Finally, we tested the significance of the fit of our simulated diversity output to our empirical Y/A ratio (\X new figure) by calculating the proportion of simulation replicates for which $\theta_{{Y}sim}$ was not significantly different from $\theta_{{Y}observed}$, using a two-sided P value. Commands for running the simulations are provided in the Supporting Information.
